---
title: "Participant Demographics"
author: "Micah E. Hirsch, M.S."
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The purpose of this document is to create a cleaned and deidentified version of the participant demographic dataset, generate a data dictionary to accompany the cleaned demographic dataset, and to compile the participant demographic information for the study "A Qualitative Exploration of Open Science Practices in Communication Sciences and Disorders" conducted by Pfeiffer et al. You can find more information posted on the study's project page on Open Science Framework (OSF). 

Link to OSF Project Page: https://osf.io/tprzu/

```{r, warning = F, message = F}

library(tidyverse) # install.packages("tidyverse")
library(rio) # install.packages("rio")
library(gtsummary) # install.packages("gtsummary")
library(gt) # install.packages("gt")
library(remotes) # install.packages("remotes")
library(LaCroixColoR) # remotes::install_github("johannesbjork/LaCroixColoR")
library(ggalluvial) # install.packages("ggalluvial")
library(ggpubr) # install.packages("ggpubr")

# Loading the datasets

demo_r1 <- rio::import("Data/Raw Data/Participant Demographics/participant_demo.xlsx", which = "R1")

demo_n_r1 <- rio::import("Data/Raw Data/Participant Demographics/participant_demo.xlsx", which = "NON-R1")

# Creating shorter variable names

header_names <- c("part_consent", "data_consent", "name", "id", "job_title", "job_title_2", "edu", "edu_2",
                  "degree_awarded", "edu_class","years_emp_current", "research_percent", "teaching_percent",
                  "service_percent", "years_emp_total", "research_exp", "current_inst_class",
                  "current_inst_class_2", "region", "research_area", "assistant_pubs", "total_pubs", "fam_os",
                  "use_os", "age", "gender", "ethnicity", "middle_eastern_text", "asian_text", "black_text",
                  "hispanic_text", "native_american_text", "pacific_islander_text", "white_text", "other_eth_text", "race", "race_text")

names(demo_r1) <- header_names

names(demo_n_r1) <- header_names

# Combining R1 and Non-R1 dfs

demo_full <- rbind(demo_r1, demo_n_r1)

# Several of the variables have different types of responses. This next section of code will clean up the responses to be in a consistent format

demo_full <- demo_full |>
  # Removing unneeded variables
  dplyr::select(-c(part_consent, data_consent, name, race_text)) |>
  # Removing a participant who signed up, but did not attend
  dplyr::filter(!is.na(id))|>
  # Recoding job title response for participant 26 and condensing edu variable
  dplyr::mutate(job_title = recode(job_title, "Other (please specify below)" = "Assistant Professor"),
                edu_2 = trimws(edu_2, "both"),
                edu = case_when(edu_2 == "MD/PhD" ~ "MD/PhD",
                                edu_2 == "M.A., currently ABD for a PhD" ~ "ABD",
                                TRUE ~ edu),
                edu = as.factor(edu)) |>
  # Cleaning Rest of the Variables
  dplyr::mutate(degree_awarded = case_when(degree_awarded == "M.A." ~ NA,
                                           degree_awarded == "PhD" ~ NA,
                                           TRUE ~ degree_awarded),
                degree_awarded = as.numeric(degree_awarded),
                edu_class = str_extract(edu_class, "^[^\\(]+"),
                edu_class = trimws(edu_class, "both"),
                edu_class = as.factor(edu_class),
                current_inst_class = str_extract(current_inst_class, "^[^\\(]+"),
                current_inst_class = trimws(current_inst_class, "both"),
                years_emp_current = trimws(years_emp_current, "both"),
                years_emp_current = case_when(years_emp_current == "4 months" ~ .33,
                                              years_emp_current == "2 years" ~ 2,
                                              years_emp_current == "0.5 yrs" ~ .5,
                                              years_emp_current == 
                                                "this university- I'm in year 1. I have been at 3 universities since 2012" ~ 1,
                                              years_emp_current == "This is my third year, but I started ABD as an instructor, so this is my second year as an assistant professor technically." ~ 2,
                                              years_emp_current == "0.5 (since August 2022)" ~ .5,
                                              years_emp_current == "&lt;1" ~ 1,
                                              years_emp_current == "3 yrs, 9 mo" ~ 3.75,
                                              TRUE ~ as.numeric(years_emp_current)),
                research_percent = gsub("%", " ", research_percent),
                research_percent = trimws(research_percent, "both"),
                research_percent = case_when(research_percent == "40  of 9-mo" ~ 40,
                                             research_percent == "it varies by semester; on average 50" ~ 50,
                                             research_percent == "20-30"~ 25,
                                             research_percent == "Probably less than 10" ~ 10,
                                             research_percent == "40  of 9 mo contract" ~ 40,
                                             research_percent == "&lt;25" ~ 25,
                                             TRUE ~ as.numeric(research_percent)),
                teaching_percent = gsub("%", " ", teaching_percent),
                teaching_percent = trimws(teaching_percent, "both"),
                teaching_percent = case_when(teaching_percent == "40  of 9-mo" ~ 40,
                                             teaching_percent == "it varies; 35  ish" ~ 35,
                                             teaching_percent == "50-60" ~ 55,
                                             teaching_percent == "50  of 9 mo" ~ 50,
                                             TRUE ~ as.numeric(teaching_percent)),
                service_percent = gsub("%", " ", service_percent),
                service_percent = trimws(service_percent, "both"),
                service_percent = case_when(service_percent == "20  of 9-mo" ~ 20,
                                            service_percent == "10  of 9 mo (5  service, 5  advising)" ~ 10,
                                            service_percent == "&lt;25" ~ 25,
                                            TRUE ~ as.numeric(service_percent)),
                years_emp_total = trimws(years_emp_total, "both"),
                years_emp_total = case_when(years_emp_total == "4 months" ~ .33,
                                            years_emp_total == "almost 6 years" ~ 6,
                                            years_emp_total == "0.5 years" ~ .5,
                                            years_emp_total == 
                                              "since 2012. I was tenured and an associate professor 1 year before arriving at my current university (came here and went back down to assistnant as I went from an R2 to an R1)" ~ 2023 - 2012,
                                            years_emp_total == "&lt;1" ~ 1,
                                            years_emp_total == "3 yrs, 9 mo" ~ 3.75,
                                            TRUE ~ as.numeric(years_emp_total)),
                research_exp = trimws(research_exp, "both"),
                research_exp = case_when(research_exp == "2 years undergrad RA + 2 yrs MS RA + 5.5 yrs PhD +0.5 assistant professor = 10 yrs" ~ 10,
                                         research_exp == "16 years" ~ 16,
                                         research_exp == "4 years of PhD + 3 years assistant professor- 1 year of overlap= 7." ~ 7,
                                         research_exp == "2 yrs GRA, 1 yr CFY with a small research component, 4 yrs PhD student, 3.75 yrs assistant prof" ~ 2+1+4+3.75,
                                         research_exp == "7 years" ~ 7,
                                         TRUE ~ as.numeric(research_exp)),
                assistant_pubs = case_when(assistant_pubs == "0 (2 submitted)" ~ 0,
                                           assistant_pubs == "20 ish" ~ 20,
                                           TRUE ~ as.numeric(assistant_pubs)),
                total_pubs = ifelse(total_pubs == "I was tenured for one year before moving- so 24ish ?", 24, as.numeric(total_pubs)),
                fam_os = case_when(fam_os == "I am not at all familiar with open science practices." ~ 1,
                                   fam_os == "I am slightly familiar with open science practices." ~ 2,
                                   fam_os == "I am somewhat familiar with open science practices." ~ 3,
                                   fam_os == "I am moderately familiar with open science practices." ~ 4,
                                   TRUE ~ 5),
                fam_os = factor(fam_os, levels = c(1, 2, 3, 4, 5),
                                labels = c("Not Familiar at All", "Slightly Familiar", "Somewhat Familiar",
                                           "Moderately Familiar", "Extremely Familiar")),
                use_os = case_when(use_os == "I do not use open science practices." ~1,
                                   use_os == "I rarely use open science practices." ~ 2,
                                   use_os == "I sometimes use open science practices." ~3,
                                   TRUE ~ 4),
                use_os = factor(use_os, levels = c(1, 2, 3, 4), 
                                labels = c("Never", "Rarely", "Sometimes", "Often")),
                age = as.numeric(age),
                gender = str_to_sentence(gender),
                gender = case_when(gender == "Female" ~ "Woman",
                                   gender == "F" ~ "Woman",
                                   gender == "Cisgender woman" ~ "Woman",
                                   gender == "Cis female" ~ "Woman",
                                   gender == "Male" ~ "Man",
                                   gender == "Cis-male" ~ "Man",
                                   is.na(gender) ~ "Prefer not to say",
                                   TRUE ~ gender),
                gender = factor(gender, levels = c("Man", "Woman", "Nonbinary", "Prefer not to say")),
                ethnicity = str_split_fixed(ethnicity, "-", n=2)[,1]) |>
  # Recoding participant 25"s response to current institution
  # They were initially unsure how to classify their current institution, but investigator determined they are R1
  dplyr::mutate(current_inst_class = case_when(id == 25 ~ "R1",
                                               TRUE ~ current_inst_class),
                current_inst_class = as.factor(current_inst_class)) |>
  # Separating the different responses for research area (some participants indicated multiple areas) 
  dplyr::mutate(research_area = gsub("Higher education, administration, and/or supervision in CSD", 
                                     "Higher education in CSD", research_area)) |>
  tidyr::separate_longer_delim(research_area, ",") |>
  dplyr::mutate(research_area = trimws(research_area, "both"))

# removing unneeded items from the environment
rm(header_names, demo_n_r1, demo_r1)

# Creating new variable called focus group (indicates whether participant attended R1 or Non-R1 meetings)
demo_full <- demo_full |>
  dplyr::mutate(focus_group = ifelse(current_inst_class == "R1", "R1", "Non-R1"), .after = id) |>
  # Editing a few more variables in the df
  dplyr::mutate(focus_group = factor(focus_group, levels = c("R1", "Non-R1")),
                region = as.factor(region),
                research_area = as.factor(research_area),
                ethnicity = as.factor(ethnicity),
                race = ifelse(race == "I prefer not to answer", "Prefer not to answer", race),
                race = factor(race, levels = c("White", "Black", "Asian", "Latino or Hispanic", "Prefer not to answer")),
                job_title = as.factor(job_title),
                id = case_when(focus_group == "R1" ~ paste("R1", id, sep = "-"),
                                 TRUE ~ paste("nR1", id, sep = "-")))

demo_full <- demo_full |>
  # removing unneeded variables (these have been recoded in the df)
  dplyr::select(-c(job_title_2, edu_2))

# Exporting a cleaned version of the participant demographics df
rio::export(demo_full, "Data/Prepped Data/Demographics/demo_cleaned.csv")

```


# Demographics

## Main Demographic Table

This is the main demographic table for the Open Science Focus group study.

```{r, warning = F, message = F}

demo_table <- demo_full |>
  dplyr::select(id, focus_group, age, gender, race, years_emp_total, research_exp, 
                region, research_percent, teaching_percent, service_percent,
                assistant_pubs, total_pubs) |>
  dplyr::distinct() |>
  dplyr::select(-id) |>
  tbl_summary(
    by = focus_group,
    type = list(service_percent ~ "continuous"),
    statistic =  list(
        all_continuous() ~ "{mean} ({sd})",
        all_categorical() ~ "{n} ({p}%)"),
    label = list(age ~ "Age",
                 gender ~ "Gender",
                 race ~ "Race",
                 years_emp_total ~ "Total Years Employed as Assistant Professor",
                 research_exp ~ "Total Years of Research Experience",
                 region ~ "Region",
                 research_percent ~ "% Research Workload",
                 teaching_percent ~ "% Teaching Workload",
                 service_percent ~ "% Service Workload",
                 assistant_pubs ~ "# of Publications as Assistant Professor",
                 total_pubs ~ "Total # of Publications"),
    missing = "no",
    digits = list(everything() ~ c(2))) |>
  as_gt()

demo_table

demo_table |>
  gt::gtsave("Tables/demo_table.html")

```


## Additional Demographic Information

These are supplemental tables providing additional information about our participants.

### Research Areas

```{r, warning = F, message = F}

R1 <- demo_full |>
  dplyr::select(id, focus_group, research_area) |>
  dplyr::filter(focus_group == "R1") |>
  dplyr::select(-focus_group) |>
  dplyr::mutate(area = T) |>
  tidyr::complete(id, research_area, fill = list(area = F)) |>
  select(-id) |>
  tbl_summary(
        by = area,
        percent = "row",
        label = list(research_area ~ "Area(s) of Study")) |>
  modify_header(stat_2 ~ "**R1**") |>
  modify_column_hide(stat_1)


Non_R1 <- demo_full |>
  dplyr::select(id, focus_group, research_area) |>
  dplyr::filter(focus_group == "Non-R1") |>
  dplyr::select(-focus_group) |>
  dplyr::mutate(area = T) |>
  tidyr::complete(id, research_area, fill = list(area = F)) |>
  select(-id) |>
  tbl_summary(
        by = area,
        percent = "row",
        label = list(research_area ~ "Area(s) of Study")) |>
  modify_header(stat_2 ~ "**Non-R1**") |>
  modify_column_hide(stat_1)

research_area_table <- tbl_merge(list(R1, Non_R1)) |>
  modify_spanning_header(everything() ~ NA_character_) |>
  as_gt()

research_area_table


```


### Education Level (Type of Doctorate Earned), Familiarity of Open Science, and Use of Open Science

```{r}

demo_2 <- demo_full |>
  dplyr::select(id, focus_group, edu, fam_os, use_os) |>
  dplyr::distinct() 

demo_2|>
  dplyr::select(-id) |>
  tbl_summary(
    by = focus_group,
    statistic =  list(all_categorical() ~ "{n} ({p}%)"),
    label = list(edu ~ "Highest Level of Education",
                 fam_os ~ "Familiarity of Open Science Practices",
                 use_os ~ "Use of Open Science Practices")) |>
  as_gt()

```



```{r, echo = F, message = F, warning = F}

rm(demo_2, demo_table, Non_R1, R1, research_area_table)

```


# Figures

## Alluvial Plot

```{r, warning = F, message = F}

# Color Palette
my_pal <- lacroix_palette("Mango", type = "discrete")

demo_full |>
  dplyr::select(-research_area) |>
  dplyr::distinct() |>
  dplyr::group_by(focus_group, region, fam_os, use_os) |>
  dplyr::summarize(n = n()) |>
  ggplot() +
  aes(y = n,
      axis1 = focus_group,
      axis2 = fam_os,
      axis3 = use_os) +
  geom_alluvium(aes(fill = focus_group), width = 1/12) +
  geom_stratum(width = 1/12, alpha = .5) +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("focus_group", "fam_os", "use_os"), 
                   labels = c("Institution Classification", "Familiarity with Open Science", "Use of Open Science"),
                   expand = c(.05, .05)) +
  scale_fill_manual(values = my_pal) +
  labs(y = "Count",
       fill = "Group") +
  theme_classic()

```


## Research Area Plot

```{r, warning = F, message = F}
research_plot <- demo_full |>
  dplyr::select(id, focus_group, research_area) |>
  dplyr::group_by(focus_group, research_area) |>
  dplyr::summarize(n = n()) |>
  ggplot() +
  aes(x = research_area,
      y = n,
      color = focus_group,
      fill = focus_group) +
  geom_bar(stat = "identity", position=position_dodge(), alpha = .5) +
  labs(title = "Research Areas",
       x = "",
       y = "Count",
       caption = "Note: Participants were able to select multiple research areas. None of the R1 participants \nhad research areas in higher education or telepractice in CSD.",
       color = "Group",
       fill = "Group") +
  scale_color_manual(values = my_pal) +
  scale_fill_manual(values = my_pal) +
  scale_y_continuous(breaks = seq( 0 ,12, by = 2)) +
  scale_x_discrete(labels = c("AAC", "Articulation/Speech Science", "Aural Rehabilitation",
                              "Cognitive-Linguistic Communication", "Cultural/Linguistic Diversity",
                              "Hearing and/or Balance", "Higher Education in CSD", "Language Learning and/or Disorders",
                              "Neurogenic Communication Disorders", "Social Aspects of Communication",
                              "Speech Sound Disorders", "Telepractice in CSD", "Voice and Resonance")) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
        plot.caption = element_text(size = 7, hjust = 1),
        aspect.ratio = .5)

research_plot

ggsave("Figures/research_area_plot.png", plot = last_plot())

```


## Familiarity and Use of Open Science

```{r, warning = F, message = F}

fam_plot <- demo_full |>
  dplyr::select(id, focus_group, fam_os) |>
  dplyr::group_by(focus_group, fam_os) |>
  dplyr::summarize(n = n()) |>
  ggplot() + 
  aes(x = fam_os,
      y = n,
      group = focus_group,
      color = focus_group,
      fill = focus_group) +
  geom_bar(stat = "identity", position=position_dodge(), alpha = .5) +
  labs(title = "Familiarity with Open Science Practices", 
       x = "", y = "Count", 
       color = "Group", fill = "Group") +
  scale_color_manual(values = my_pal) +
  scale_fill_manual(values = my_pal) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1),
        aspect.ratio = 1)

fam_plot


```


## Use of Open Science

```{r, warning = F, message = F}

use_plot <- demo_full |>
  dplyr::select(id, focus_group, use_os) |>
  dplyr::group_by(focus_group, use_os) |>
  dplyr::summarize(n = n()) |>
  ggplot() + 
  aes(x = use_os,
      y = n,
      group = focus_group,
      color = focus_group,
      fill = focus_group) +
  geom_bar(stat = "identity", position=position_dodge(), alpha = .5) +
  labs(title = "Use of Open Science Practices", 
       x = "", y = "Count", 
       color = "Group", fill = "Group") +
  scale_color_manual(values = my_pal) +
  scale_fill_manual(values = my_pal) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1),
        aspect.ratio = 1)

use_plot

```



```{r, eval = F, warning = F, message = F}

# Combining the ratings plot

ratings_plot <- ggpubr::ggarrange(fam_plot, use_plot, ncol = 2, align = "h", common.legend = T, legend = "bottom")

ggpubr::annotate_figure(ratings_plot, bottom = text_grob("Note: None of the participants from the Non-R1 group indicated they were 'extremely familiar' with open science practices.", hjust = 1, x = 1, face = "italic", size = 6))

ggsave("Figures/ratings_plot.png", plot = last_plot())
```



```{r, echo = F, warning = F, message = F}

# Creating a Data Dictionary

library(datadictionary)

labels <- c(id = "Participant ID",
            focus_group = "Focus Group Assignment",
            job_title = "Job Title",
            edu = "Highest Education Level",
            degree_awarded = "Year Highest Degree was Awarded",
            edu_class = "Carnegie Classification of Training Institution",
            years_emp_current = "Years Employed in Current Position",
            research_percent = "Percent Workload Dedicated to Research",
            teaching_percent = "Percent Workload Dedicated to Teaching",
            service_percent = "Percent Workload Dedicated to Service",
            years_emp_total = "Total Years Employed as an Assistant Professor",
            research_exp = "Total Years of Research Experience",
            current_inst_class = "Carnegie Classification of Current Institution",
            current_inst_class_2 = "Current Institution Classification (write-in option)",
            region = "Regional Location of Current Institution",
            research_area = "Participant Research Area(s)",
            assistant_pubs = "Number of Publications as an Assistant Professor",
            total_pubs = "Total Number of Publications",
            fam_os = "Familiarity with Open Science Practices",
            use_os = "Use of Open Science Practices",
            age = "Age",
            gender = "Gender",
            ethnicity = "Ethnicity",
            middle_eastern_text = "Middle Eastern (write in option to specify)",
            asian_text = "Asian (write in option to specify)",
            black_text = "Black (write in option to specify)",
            hispanic_text = "Hispanic (write in option to specify)",
            native_american_text = "Native American (write in option to specify)",
            pacific_islander_text = "Pacific Islander (write in option to specify)",
            white_text = "white (write in option to specify",
            other_eth_text = "Other ethnicity (write in option to specify)",
            race = "Race")

data_dict <- create_dictionary(demo_full, var_labels = labels)

rio::export(data_dict, "Data/Prepped Data/Demographics/demo_cleaned_dictionary.csv")


```

